Pyg4ometry: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-08-29 public/paper/pyg4ometry.tex
Comment out large and rather redundant table

\begin{table}[hbt!]
\centering
\begin{tabular}{ l l l } \hline
GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
Define 			& Constant				& gdml.Constant				\\
				& Variable					& gdml.Variable					\\
				& Quantity					& gdml.Quantity				\\
				& Expression 				& gdml.Expression				\\
				& Position					& gdml.Position					\\
				& Rotation					& gdml.Rotation				\\
				& Scale					& gdml.Scale					\\
				& Matrix					& gdml.Matrix					\\ \hline
Materials 			& Element					& geant4.Element				\\
				& Isotope					& geant4.Isotope				\\
				& Material					& geant4.Material				\\ \hline
Solid  			& Box					& geant4.solid.Box				\\
	  			& Tube					& geant4.solid.Tubs				\\
	  			& CutTube				& geant4.solid.CutTubs			\\
	  			& Cone					& geant4.solid.Cons				\\
	  			& Para					& geant4.solid.Para				\\
	  			& Trd					& geant4.solid.Trd				\\
	  			& Trap					& geant4.solid.Trap				\\
	  			& Sphere					& geant4.solid.Sphere			\\
	  			& Orb					& geant4.solid.Orb				\\
	  			& Torus					& geant4.solid.Torus				\\
	  			& Polycone				& geant4.solid.Polycone			\\
	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
	  			& Polyhedra				& geant4.solid.Polyhedra			\\
				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
	  			& Eltube					& geant4.solid.EllipticalTube		\\
	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
	  			& Elcone					& geant4.solid.EllipticalCone		\\
				& Paraboloid				& geant4.solid.Paraboloid			\\
				& Hype					& geant4.solid.Hyperboloid		\\
				& Tet						& geant4.solid.Tet				\\
				& Xtru					& geant4.solid.ExtrudedSolid		\\
				& TwistedBox				& geant4.solid.TwistedBox		\\
				& TwistedTtap				& geant4.solid.TwistedTrap		\\
				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
				& TwistedTube				& geant4.solid.TwistedTube		\\
				& Arb8					& geant4.solid.GenericTrap		\\
				& Tessellated				& geant4.solid.TessellatedSolid 	\\
				& Union					& geant4.solid.Union				\\
				& Subtraction				& geant4.solid.Subtraction			\\
				& Intersection				& geant4.solid.Intersection 		\\
				& MultiUnion				& geant4.solid.MultiUnion 			\\
				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
Structure			& Volume					& geant4.LogicalVolume			\\
				& Assembly				& geant4.AssemblyVolume 		\\
				& PhysVol					& geant4.PhysicalVolume			\\ 
				& ReplicaVol				& geant4.ReplicaVolume			\\ 
				& ParaVol					& geant4.ParameterisedVolume	\\ 
				& DivisionVol				& geant4.DivisionVolume			\\
				& SkinSurface				& geant4.SkinSurface			\\ 
				& BorderSurface			& geant4.BorderSurface			\\ \hline

\end{tabular}
\label{tab:gdml-tags}
\caption{GDML tags and corresponding pyg4ometry classes.}
\end{table}

>>>>

%\begin{table}[hbt!]
%\centering
%\begin{tabular}{ l l l } \hline
%GDML tag 		& Child tags				& pyg4ometry class 				\\ \hline
%Define 			& Constant				& gdml.Constant				\\
%				& Variable					& gdml.Variable					\\
%				& Quantity					& gdml.Quantity				\\
%				& Expression 				& gdml.Expression				\\
%				& Position					& gdml.Position					\\
%				& Rotation					& gdml.Rotation				\\
%				& Scale					& gdml.Scale					\\
%				& Matrix					& gdml.Matrix					\\ \hline
%Materials 			& Element					& geant4.Element				\\
%				& Isotope					& geant4.Isotope				\\
%				& Material					& geant4.Material				\\ \hline
%Solid  			& Box					& geant4.solid.Box				\\
%	  			& Tube					& geant4.solid.Tubs				\\
%	  			& CutTube				& geant4.solid.CutTubs			\\
%	  			& Cone					& geant4.solid.Cons				\\
%	  			& Para					& geant4.solid.Para				\\
%	  			& Trd					& geant4.solid.Trd				\\
%	  			& Trap					& geant4.solid.Trap				\\
%	  			& Sphere					& geant4.solid.Sphere			\\
%	  			& Orb					& geant4.solid.Orb				\\
%	  			& Torus					& geant4.solid.Torus				\\
%	  			& Polycone				& geant4.solid.Polycone			\\
%	  			& GenericPolycone			& geant4.solid.GenericPolycone	\\
%	  			& Polyhedra				& geant4.solid.Polyhedra			\\
%				& GenericPolyhedra                  & geant4.solid.GenericPolyhedra	\\ 
%	  			& Eltube					& geant4.solid.EllipticalTube		\\
%	  			& Ellipsoid					& geant4.solid.Ellipsoid			\\
%	  			& Elcone					& geant4.solid.EllipticalCone		\\
%				& Paraboloid				& geant4.solid.Paraboloid			\\
%				& Hype					& geant4.solid.Hyperboloid		\\
%				& Tet						& geant4.solid.Tet				\\
%				& Xtru					& geant4.solid.ExtrudedSolid		\\
%				& TwistedBox				& geant4.solid.TwistedBox		\\
%				& TwistedTtap				& geant4.solid.TwistedTrap		\\
%				& TwistedTrd				& geant4.solid.TwistedTrd 		\\
%				& TwistedTube				& geant4.solid.TwistedTube		\\
%				& Arb8					& geant4.solid.GenericTrap		\\
%				& Tessellated				& geant4.solid.TessellatedSolid 	\\
%				& Union					& geant4.solid.Union				\\
%				& Subtraction				& geant4.solid.Subtraction			\\
%				& Intersection				& geant4.solid.Intersection 		\\
%				& MultiUnion				& geant4.solid.MultiUnion 			\\
%				& ScaledSolid				& geant4.solid.ScaledSolid		\\				
%	  			& OpticalSurface			& geant4.solid.OpticalSurface		\\ \hline
%Structure			& Volume					& geant4.LogicalVolume			\\
%				& Assembly				& geant4.AssemblyVolume 		\\
%				& PhysVol					& geant4.PhysicalVolume			\\ 
%				& ReplicaVol				& geant4.ReplicaVolume			\\ 
%				& ParaVol					& geant4.ParameterisedVolume	\\ 
%				& DivisionVol				& geant4.DivisionVolume			\\
%				& SkinSurface				& geant4.SkinSurface			\\ 
%				& BorderSurface			& geant4.BorderSurface			\\ \hline
%
%\end{tabular}
%\label{tab:gdml-tags}
%\caption{GDML tags and corresponding pyg4ometry classes.}
%\end{table}
